On the effects of partying on next-day sports performance

### 2017-06-14 writing/draft.tex
Fixed camel-casing in (sub)section titles.

\subsection{Individual Players}
Studies have also been carried out on statistical ranking of the players
most notorious for pursuing active nightlife in the NBA.\citep{chase} In particular, 
the author rejects the null hypothesis that J.R. Smith shoots just as well on Sundays as he does
every other day of the week at the $p=0.01$ level of significance; however, the author also
cautions that with so many players in the NBA, it is expected that we find a split as extreme
as J.R.'s simply due to chance.
The study goes on to look
at historical performance for all NBA players who began their career after 1974, and compares
Sunday afternoon performance to overall career performance. A binomial test is carried out, and the 
study concludes with strong statistical significance that across the NBA, 
individual players perform worse on Sundays when compared with other days, 
as measured by the ratio of shots scored to shots taken.

@@

\subsection{Laboratory Studies}
Studies on effects of alcohol on sports performance in a controlled setting
show that alcohol impairs the nervous system, resulting in a decline in both
cognitive function and motor skill.\citep{shirreffs} In a study on 
the effects of alcohol on recovery of male athletes, it was found that
consumption is correlated with reduced production of testosterone
which ultimately leads to inhibited ability to recover and adapt to exercise.\citep{mjbarnes}
Sleep deprivation has also been shown to strongly impair cognitive and motor performance.\citep{pilcher} Both alcohol and sleep deprivation are well correlated with nightlife.

@@

\subsection{Modeling Approach}

@@

\subsubsection{Placebo Tests} As a sanity check with our NBA data, we interact a
discrete-indicator for Los Angeles and New York with an 
indicator for \emph{more} than 24 hours of rest
between games, and call this our placebo effect. The only difference between this feature
and our discrete indicator for nightlife is the time-window of interest.
The idea is that with sufficient rest time, the hangover effect dissipates.

@@

\subsection{Possible Confounders or potential issues}

>>>>

\subsection{Individual players}
Studies have also been carried out on statistical ranking of the players
most notorious for pursuing active nightlife in the NBA.\citep{chase} In particular, 
the author rejects the null hypothesis that J.R. Smith shoots just as well on Sundays as he does
every other day of the week at the $p=0.01$ level of significance; however, the author also
cautions that with so many players in the NBA, it is expected that we find a split as extreme
as J.R.'s simply due to chance.
The study goes on to look
at historical performance for all NBA players who began their career after 1974, and compares
Sunday afternoon performance to overall career performance. A binomial test is carried out, and the 
study concludes with strong statistical significance that across the NBA, 
individual players perform worse on Sundays when compared with other days, 
as measured by the ratio of shots scored to shots taken.

@@

\subsection{Laboratory studies}
Studies on effects of alcohol on sports performance in a controlled setting
show that alcohol impairs the nervous system, resulting in a decline in both
cognitive function and motor skill.\citep{shirreffs} In a study on 
the effects of alcohol on recovery of male athletes, it was found that
consumption is correlated with reduced production of testosterone
which ultimately leads to inhibited ability to recover and adapt to exercise.\citep{mjbarnes}
Sleep deprivation has also been shown to strongly impair cognitive and motor performance.\citep{pilcher} Both alcohol and sleep deprivation are well correlated with nightlife.

@@

\subsection{Modeling approach}

@@

\subsubsection{Placebo tests} As a sanity check with our NBA data, we interact a
discrete-indicator for Los Angeles and New York with an 
indicator for \emph{more} than 24 hours of rest
between games, and call this our placebo effect. The only difference between this feature
and our discrete indicator for nightlife is the time-window of interest.
The idea is that with sufficient rest time, the hangover effect dissipates.

@@

\subsection{Possible confounders or potential issues}
